\mythesistitleNOTSYNPOSIS \tnote[fyi]{Synopsis title is ``Generalization of Consecutive Ones Property of Binary Matrices''}

### 2012-02-02 src/0031ded.tex
* Regular edits. See diff for changes.
* Formatting/layout related changes. stuff i'll forget later.
-------
basically:
- added two side printing
- added headers
- added tag/label markers for draft
- made all chapters/chapter*s start on odd page

technically:
- Added contents to Toc
- increased vglue in ded.tex. adjusted one hspace too. to make them fit in.
- began adding short titles for Toc. (chapter 2)
- added twoside option in LoadClass
- adjusted margins in \RequirePackage{geometry} - reduced left margin. otherwise doc bloats up with a lot of margin whitespace on twoside.
- added headings

\definecolor{dim}{rgb}{0.7,0.7,0.7}
\def \dimspace {0.125in}

{%
  \fontencoding{T1}%
  \fontfamily{bch} %{put} %{bch} % {pbk} % \fontfamily{cmdh}
  % \fontfamily{pag}
  \selectfont%

  \vglue -0.5in % this makes top margin 2in
%   \vskip -5ex%
%   \hspace{5in}\parbox{1in}{\raggedright Hello world}

  \hspace{-1in}%
  \parbox[c]{4in}{%
    \large \raggedright \noindent %
    \color{dim}{%
      The process of preparing programs for the digital computer is
      especially attractive, not only because it can be economically
      and scientifically rewarding, but also because it can be an
      aesthetic experience much like composing poetry or music.%
      {%
        \small \par \hfill \emph{The Art of Computer Programming},
        D.\,E.\,K.%
      }%
    }%
  }%

  \vspace{\dimspace}

  \hspace{1.5in}%
  \parbox[t]{4in}{%
    \Large \noindent \raggedleft%
    \color{dim}{%
      The rhetoric and mythos of science create the comforting image
      of linear progression toward truth.%
      {%
        \small \par \hfill%
        \textbf{mythos}; \emph{New Oxford American Dictionary, 2nd
          Ed.}%
      }%
    }%
  }
  \\
  \vspace{\dimspace}

  % \hspace{1in}
  {\centering
    \parbox{6in}{%
%      \Huge 
      \fontsize{27}{1.5}\selectfont
      \centering \noindent %
%      \textbf{
      \emph{L'art c'est la solution au chaos.} \par \noindent
      \noindent (Art is the solution to chaos.)
%      }
%       {%
%         \small \par \hfill%
%         \emph{citation needed.}%
%       }%
    }%
  }%

  \vspace{\dimspace}

  \hspace{-0.25in}%
  \parbox{2.5in}{%
    \Large 
    \raggedright \noindent%
    \color{dim}{%
      Kilroy wasn't Haar.  Free the group.  Nuke the kernel.  Power to
      the $n$.  $N = 1 \Rightarrow P = NP$ %
    }%
    {%
      \small \par \hfill%
      \emph{Concrete Mathematics}%
    }%
  }%
  \vspace{\dimspace}

  \hspace{1in}%
  \parbox{5in}{%
    \large \raggedleft \noindent%
    \color{dim}{%
      Anything that happens, happens.  Anything that, in happening,
      causes something else to happen, causes something else to
      happen.  Anything that, in happening, causes itself to happen
      again, happens again.  It doesn't necessarily do it in
      chronological order, though.  }%
    {%
      \small \par \hfill%
      \emph{The Salmon of Doubt}, D.\,N.\,A.%
    }%
  }%
  \vspace{\dimspace}

  \hspace{-0.50in}%
  \parbox{4in}{%
    \huge \noindent \raggedright%
    \color{dim}{%
      This is water, this is water.%
      {%
        \small \par \hfill%
        D.\,F.\,W.%
      }%
    }%
  }%

}

>>>>

\xclearpage

{% 
  \thispagestyle{empty}%
  \parbox[c]{\linewidth}%
  {%
    \vspace{0.5\linewidth}% 
    \centering% 
    % To you, Z., for your patience.%
    \large%
    {\em For Z.}%
  }%
}%

### 2012-02-02 src/010chap1.tex
-- sent to n for review
- moved ded to quot. added ded.
- pqtree, pctree figures completed.
- fixed a few missing bibs
- random clean up including temptexts. see diff.

Once a matrix has been detected to not have COP (using any of the COT
algorithms mentioned earlier), it is naturally of interest to find out
the smallest forbidden substructure (in terms of number of rows and/or
columns and/or number of entries that are {\un}s). \cite{d08phd}
discusses a couple of algorithms which are efficient if the number of
{\un}s in a row is small. This is of significance in the case of
sparse matrices where this number is much lesser than the number of
columns. $(*,\Delta)${\em -matrices} are matrices with no restriction
on number of {\un}s in any column but have at most $\Delta$ {\un}s in
any row. {\sc Min COS-R (Min COS-C), Max COS-R (Max COS-C)} are
similar problems which deals with inducing COP on a matrix. In {\sc
  Min COS-R (Min COS-C)} the question is to find the minimum number of
rows (columns) that must be deleted to result in a matrix with COP.
In the dual problem {\sc Max COS-R (Max COS-C)} the search is for the
maximum number of rows (columns) that induces a submatrix with
COP. Given a matrix $M$ with no COP, \cite{b75-phd} shows that finding
a submatrix $M'$ with all columns\temptext{ check if b75 deals with
  COP col or COP row. also is it any submatrix with k less than r rows
  or submatrix must have all columns? } but a maximum cardinality
subset of rows such that $M'$ has COP is NP complete. \cite{hg02}
corrects an error of the abridged proof of this reduction as given in
\cite{gj79}.  \cite{d08phd} discusses all these problems in detail
giving an extensive survey of the previously existing results which
are almost exhaustively all approximation results and hardness
results. Taking this further, \cite{d08phd} presents new results in
the area of parameterized algorithms for this
problem.

Another problem is to find the minimum number of entries in the matrix
that can be toggled to result in a matrix with COP.  \cite{v85}
discusses approximation of {\sc COP Augmentation} which is the problem
of changing of the minimum number of zero entries to {\un}s so that
the resulting matrix has COP. As mentioned earlier, this problem is
known to be NP complete due to \cite{b75-phd}. \cite{v85} also proves,
using a reduction to the longest path problem, \temptext{ or is it a
  survey of another result?  check.} that finding a Tucker's forbidden
submatrix of at least $k$ rows is NP complete. \temptext{ how is this
  different from booth's 75 result??}

>>>>

Once a matrix has been detected to not have COP (using any of the COT
algorithms mentioned earlier), it is naturally of interest to find out
the smallest forbidden substructure (in terms of number of rows and/or
columns and/or number of entries that are {\un}s). \cite{d08phd}
discusses a couple of algorithms which are efficient if the number of
{\un}s in a row is small. This is of significance in the case of
sparse matrices where this number is much lesser than the number of
columns. $(*,\Delta)${\em -matrices} are matrices with no restriction
on number of {\un}s in any column but have at most $\Delta$ {\un}s in
any row. {\sc Min COS-R (Min COS-C), Max COS-R (Max COS-C)} are
similar problems which deals with inducing COP on a matrix. In {\sc
  Min COS-R (Min COS-C)} the question is to find the minimum number of
rows (columns) that must be deleted to result in a matrix with COP.
In the dual problem {\sc Max COS-R (Max COS-C)} the search is for the
maximum number of rows (columns) that induces a submatrix with
COP. Given a matrix $M$ with no COP, \cite{b75-phd} shows that finding
a submatrix $M'$ with all columns but a maximum cardinality
subset of rows such that $M'$ has COP is NP complete. \cite{hg02}
corrects an error of the abridged proof of this reduction as given in
\cite{gj79}.  \cite{d08phd} discusses all these problems in detail
giving an extensive survey of the previously existing results which
are almost exhaustively all approximation results and hardness
results. Taking this further, \cite{d08phd} presents new results in
the area of parameterized algorithms for this
problem.

Another problem is to find the minimum number of entries in the matrix
that can be toggled to result in a matrix with COP.  \cite{v85}
discusses approximation of {\sc COP Augmentation} which is the problem
of changing of the minimum number of zero entries to {\un}s so that
the resulting matrix has COP. As mentioned earlier, this problem is
known to be NP complete due to \cite{b75-phd}. \cite{v85} also proves,
using a reduction to the longest path problem, that finding a Tucker's
forbidden submatrix of at least $k$ rows is NP complete.
